\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{titlesec, tabularx, array, xcolor, enumitem, hyperref, paracol}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{charter}
\usepackage{fontawesome5}

% Custom Colors
\definecolor{primaryColor}{RGB}{0, 0, 0}

% Formatting:
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.2cm}
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$} 

% Section Title Style
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{2pt}\titlerule]

\begin{document}

% HEADER
\begin{center}
    {\LARGE\bfseries Franco Exequiel Becvort} \\
    Lisbon, Portugal | Open to relocation | Work permit required \\
    \href{mailto:franbecvort@gmail.com}{franbecvort@gmail.com} | 
    \href{https://pollito.dev/}{pollito.dev} | 
    \href{https://linkedin.com/in/franco-becvort}{linkedin.com/in/franco-becvort} \\
\end{center}

\vspace{5pt}

% PROFESSIONAL SUMMARY
\section{Profile}
Experienced Software Developer with a strong foundation in designing and scaling high-performance Java Spring Boot microservices for enterprise and fintech applications. Proven expertise in multi-cloud deployment (GCP, Azure) and complex authentication systems. Currently leveraging modern full-stack technologies (TypeScript, React, Deno) to develop innovative solutions in the rapidly evolving domain of AI and large codebase analysis. Certified in major cloud platforms and Agile methodologies.

% EXPERIENCE
\section{Experience}
\textbf{Software Developer (AI/Code Analysis), Devsu} \hfill Nov 2025 – Present \
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item Developing a new solution focused on analyzing massive codebases.
    \item Tech used: TypeScript, React, Deno, Supabase, RabbitMQ, Tailwind CSS, Vite, Docker Compose, Langfuse, LiteLLM.
\end{itemize}

\textbf{Java Spring Boot Developer, Devsu} \hfill May 2023 – October 2025 \
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item Integrated identity providers with customer facing pages and application of Ecuador’s largest private bank.
    \item Tech used: Java, Spring Boot, Google Cloud, Microsoft Azure, PostgreSQL, Redis.
\end{itemize}

\textbf{Java Spring Boot Developer, Applica Solutions} \hfill Nov 2022 – Apr 2023 \
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item Standardized the backend REST APIs for Argentina’s first QR-based payment system.
    \item Tech used: Java, Spring Boot, Oracle Database, WildFly Server.
\end{itemize}

\textbf{Next.js Developer, runaID} \hfill Jul 2022 – Oct 2022 \
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item Implemented the creation of a new auditing dashboard from scratch to process and verify huge volumes of medical receipts.
    \item Tech used: Next.js, React, TypeScript, Tailwind CSS, Node.js, Docker Compose, MySQL.
\end{itemize}

\textbf{Apache Groovy Developer, runaID} \hfill Sep 2021 – Jun 2022 \
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item Developed and maintained public services and legacy system for the San Luis city government.
    \item Tech used: Groovy Server Pages, JavaScript, jQuery, Bootstrap CSS, Apache Tomcat, Microsoft SQL Server.
\end{itemize}

\textbf{Academic Researcher, Universidad Nacional de San Luis} \hfill Jun 2020 – Jun 2022 \
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item Part of cybersecurity awareness initiatives and delivered educational talks.
    \item Admission tutor and student mentor.
\end{itemize}

% CERTIFICATIONS
\section{Certifications}
\begin{itemize}[leftmargin=10pt, noitemsep]
    \item \textbf{Microsoft Certified: DevOps Engineer Expert} – Microsoft (Oct 2025)
    \item \textbf{Microsoft Certified: Azure Developer Associate} – Microsoft (Jul 2025)
    \item \textbf{Seminário de Desempenho e Segurança do MySQL em Lisboa} – Oracle (Oct 2024)
    \item \textbf{Participação no evento Tech O'Clock 2024} – ITSector (Sep 2024)
    \item \textbf{Microsoft Certified: Azure Fundamentals} – Microsoft (Jul 2024)
    \item \textbf{Confluent Fundamentals Accreditation} – Confluent (Jun 2024)
    \item \textbf{Professional Scrum Master (PSM I)} – Scrum.org (May 2024)
    \item \textbf{Professional Cloud Architect} – Google Cloud (Mar 2024)
    \item \textbf{Associate Cloud Engineer} – Google Cloud (Nov 2023)
    \item \textbf{Cloud Computing} – Google Digital Academy (Skillshop) (Sep 2023)
    \item \textbf{EF SET Certificate English C2 Proficient} – EF Education First (Feb 2023)
    \item \textbf{Fundamentos de Spring Framework para Java} – UTN Buenos Aires (Aug 2022)
    \item \textbf{Cloud Digital Leader} – Google Cloud (May 2022)
    \item \textbf{I Jornada de Informática} – Universidad Nacional de San Luis (Nov 2019)
\end{itemize}

\end{document}

